---
title: "My master thesis"
author: "Helene Sandsten"
date: "4/26/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 12, fig.height = 8, show_col_types = FALSE)
source("R scripts/ThreeD_load_packages.R")
source("R scripts/ThreeD_create_metadata.R")
source("R scripts/aboveground_biomass.R")
source("R scripts/roots.R")
source("R scripts/teabags.R")
source("R scripts/soil.R")
```


# METHODS


... All response varibles (y) were fitted with the five following linear models:

1. y ~ warming * nitrogen * grazing 
2. y ~ warming + nitrogen + grazing 
3. y ~ warming * nitrogen + grazing 
4. y ~ warming + nitrogen * grazing 
5. y ~ warming * grazing + nitrogen 




```{r, nitrogen-table, echo = FALSE}
knitr::kable(nitrogen_table[,],
             format = "markdown",
             caption = "caption caption caption.")
```



```{r, model-table, echo = FALSE}
models_table %>% 
  kable(booktabs = T, 
        caption = "Overview of the linear models that were run ") %>%
  kable_styling()
```



```{r, data-var-table, echo = FALSE}
data_variable_table %>% 
  kable(booktabs = T, 
        caption = "This is my data variable table and this might be too much") %>%
  kable_styling()
```


# RESULTS


Warming and nitrogen had significant effects on production, both above and belowground, although not at both sites. Grazing did not have any significant effect on any of the response variables in any models.  


## 3.1 Aboveground biomass


The model that best explained the response of aboveground biomass was model 3, `aboveground biomass ~ warming * nitrogen + grazing` (see table X). Aboveground productivity significantly increased with warming (p-value = 0.0203, std.error = 0.2977) and warming when in interaction with nitrogen (p-value = 0.0081, std.error = 0.1153), although only in plots that originated from the alpine site, Liahovden. There was no significant change in aboveground biomass in plots that originated from the sub-alpine site, Joasete.   



```{r, mod-comp-agb, echo = FALSE}
## table of model comparison roots 
knitr::kable(model_comparison_agb[,],
             format = "markdown",
             caption = "Performance and comparison of models that include warming, nitrogen and grazing as explanatory variables for the response of aboveground biomass production.")
```


```{r, best-mod-op-agb, echo = FALSE}
## table of model output form best fitted model
# knitr::kable(clean_output.model.agb[,],
#              format = "markdown",
#              caption = "Output from model that performed best, aboveground biomass ~ w * n + g.")

## neat table with bold significant rows, except intercept
clean_output.model.agb %>% 
  kable(booktabs = T, 
        caption = "Output from model that performed best, aboveground biomass ~ warming * nitrogen + grazing.") %>%
  kable_styling() %>%
  row_spec(which(clean_output.model.agb$p.value < 0.05001 & 
                   clean_output.model.agb$term != "Intercept (no N, no warming, no grazing)"),
           bold = T) 
```




## 3.2 Belowground biomass


The model that best explained belowground productivity was model 2, the additive model: `belowground biomass ~ warming + nitrogen + grazing` (see table x). Root growth significantly decreased with nitrogen, although only at the sub-alpine site, Joasete. 



```{r, mod-comp-roots, echo = FALSE}
## table of model comparison roots 
knitr::kable(model_comparison_roots[,], 
             format = "markdown",
             caption = "Performance and comparison of models that include warming, nitrogen and grazing as explanatory variables for the response of fine root production.")
```


```{r, best-mod-op-roots, echo = FALSE}
## table of model output form best fitted model
# knitr::kable(clean_output.model.roots[,], 
#              format = "markdown",
#              caption = "Table 2. Model output from best model: roots ~ warming + nitrogen + grazing.")

## neat table with bold significant rows, except intercept
clean_output.model.roots %>% 
  kable(booktabs = T, 
        caption = "Output from model that performed best, root biomass~~warming + nitrogen + grazing.") %>%
  kable_styling() %>%
  row_spec(which(
    clean_output.model.roots$p.value < 0.05001 &
      clean_output.model.roots$term != "Intercept (no N, no warming, no grazing)"),
    bold = T) 
```




## 3.3 Decomposition


Insert:

1. **Model comparison (table)** 
2. **Best model output (table)** 
3. **Figure** - *with prediction lines?*
4. **Text**


```{r, echo = FALSE}
## table of model comparison roots 
#knitr::kable(model_comparison_decomp[,], format = "markdown")
```


```{r, echo = FALSE}
## table of model output form best fitted model
#knitr::kable(clean_output.model.decomp[,], format = "markdown")
```




## 3.4 Soil organic matter


The model that best explained the response of soil organic matter content was the additive model, `soil organic matter ~ w + n + g`. Soil organic matter content significantly decreased with warming in plots that originated from both the alpine (Liahovden) and subalpine site (Joasete).   



```{r, echo = FALSE, message = FALSE}
## table of model comparison soil 
knitr::kable(model_comparison_soil[,], 
             format = "markdown",
             caption = "Performance and comparison of models that include warming, nitrogen and grazing as explanatory variables for the response of proportion of soil organic matter.")
```


```{r, echo = FALSE, message = FALSE}
## table with output from model with best fit 
## neat table with bold significant rows, except intercept
clean_output.model.soil %>% 
  kable(booktabs = T, 
        caption = "Output from model that performed best, soil organic matter ~~ warming + nitrogen + grazing.") %>%
  kable_styling() %>%
  row_spec(which(
    clean_output.model.soil$p.value < 0.05001 &
      clean_output.model.soil$term != "Intercept (no N, no warming, no grazing)"),
    bold = T) 
```




## Figures


Even though the naturally grazed plots were not included in the models, I wanted to see what effect warming, nitrogen and grazing had on all the grazing levels (control, medium, intensive and natural) and compare them.  


```{r, plot-agb, echo = FALSE, message = FALSE, fig.cap = "Different aboveground biomass productivity when treated with different levels of warming, nitrogen addition and grazing"}
plot_agb_wng
```



```{r, fig-roots-wng, echo = FALSE, message = FALSE, fig.cap = "Root growth (per cm3) and the effects of warming and nitrogen."}
plot_roots_wng
```



```{r, echo = FALSE}
#plot_decomp_wng
```



```{r, echo = FALSE, message = FALSE, fig.cap = "Proportion of soil organic matter (per sample) and the effects of warming and nitrogen."}
plot_soil_wng
```


-----
