---
title: "My master thesis"
author: "Helene Sandsten"
date: "4/26/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 12, fig.height = 8)
source("R scripts/ThreeD_load_packages.R")
source("R scripts/ThreeD_create_metadata.R")
source("R scripts/roots.R")
```


# Results


This is my results section.  

Here I'll put a nice little paragraph that sums up my findings. 


## 3.1 Aboveground biomass


Insert:

1. **Model comparison (table)** 
2. **Best model output (table)** 
3. **Figure** - *with prediction lines?*



#### Table X, model comparison. 
```{r, echo = FALSE}
## table of model comparison roots 
# knitr::kable(model_comparison_XXX[,], 
#              format = "markdown",
#              caption = "Table 1. This is my caption for this table.")
```

#### Table Y, model output of model y ~ x. 
```{r, echo = FALSE}
## table of model output form best fitted model
# knitr::kable(clean_output.model.XXX[,],
#              format = "markdown",
#              caption = "Table 2 - This is my table caption")
```

## Figure of XXX 
```{r, echo = FALSE, fig.cap = "This is the caption for my figure."}
#plot_XXX_wng
```



## 3.2 Belowground biomass


The model with the best fit was model #2 `roots ~ warming + nitrogen + grazing` (*see table X*). The model output from model #2 showed that nitrogen was the only predictor variable that significantly affected root growth, and only at the sub-alpine site, Joasete (*see table Y*).


```{r, mod-comp-roots, echo = FALSE}
## table of model comparison roots 
knitr::kable(model_comparison_roots[,], 
             format = "markdown",
             caption = "Table 1. Output from model performance.")

```

#### Table Y, test. 
```{r, mod-output-roots, echo = FALSE}
## table of model output form best fitted model
knitr::kable(clean_output.model.roots[,], 
             format = "markdown",
             caption = "Table 2. Model output from best model: roots ~ warming + nitrogen + grazing.")

# https://rdrr.io/cran/kableExtra/man/row_spec.html
# row_spec(table_x, 3, bold = TRUE)
```

## Figure of roots 
```{r, fig-roots-wng, echo = FALSE, message = FALSE, fig.cap = "Figure 1 - Root growth (per cm3) and the effects of warming and nitrogen."}
plot_roots_wng
```



## 3.3 Decomposition

Insert:

1. **Model comparison (table)** 
2. **Best model output (table)** 
3. **Figure** - *with prediction lines?*


#### Table X, model comparison. 
```{r, echo = FALSE}
## table of model comparison roots 
#knitr::kable(model_comparison_XXX[,], format = "markdown")
```

#### Table Y, model output of model y ~ x. 
```{r, echo = FALSE}
## table of model output form best fitted model
#knitr::kable(clean_output.model.XXX[,], format = "markdown")
```

## Figure of XXX 
```{r, echo = FALSE}
#plot_XXX_wng
```



## 3.4 Soil organic matter


Insert:

1. **Model comparison (table)** 
2. **Best model output (table)** 
3. **Figure** - *with prediction lines?*



#### Table X, model comparison. 
```{r, echo = FALSE}
## table of model comparison roots 
#knitr::kable(model_comparison_XXX[,], format = "markdown")
```

#### Table Y, model output of model y ~ x. 
```{r, echo = FALSE}
## table of model output form best fitted model
#knitr::kable(clean_output.model.XXX[,], format = "markdown")
```

## Figure of XXX 
```{r, echo = FALSE}
#plot_XXX_wng
```



-----


# For other sections of the thesis


### Nitrogen table
```{r, nitrogen-table, echo = FALSE}
nitrogen_table <- tibble(
  "Block" = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
  "N level" = c(1,6,5,3,10,7,4,8,9,2),
  "N kg/ha/y" = c(0, 5, 1, 0, 150, 10, 0.5, 50, 100, 0))

knitr::kable(nitrogen_table[,], format = "markdown") 

```



---

https://github.com/biostats-r/quartothesis


# Neat things in markdown


# Header 1


## Header 2


### Header 3


#### Header 4


##### Header 5


###### Header 6





* **Bold text** when you wrap text in ** on each side.  

* *Italic text* when you wrap text in * on each side.  

* ***Bold and italic text*** when you wrap text in *** on each side.  

* ~~Strikethough~~ when you wrap text in ~~ on each side.  


# Code chunk options

`include = FALSE` prevents code and results from appearing in the finished file. R Markdown still runs the code in the chunk, and the results can be used by other chunks.  

`echo = FALSE` prevents code, but not the results from appearing in the finished file. This is a useful way to embed figures.  

`message = FALSE` prevents messages that are generated by code from appearing in the finished file.  

`warning = FALSE` prevents warnings that are generated by code from appearing in the finished.  

`fig.cap = "..."` adds a caption to graphical results.  



# Global options

To set global options that apply to every chunk in your file, call `knitr::opts_chunk$set` in a code chunk. `Knitr` will treat each option that you pass to `knitr::opts_chunk$set` as a global default that can be overwritten in individual chunk headers.